\Large \bf Uncovering Bugs in Distributed Storage Systems\\during Testing (not in Production!)

### 2016-01-24 paper.tex
updates

\section{Case Study: Azure Storage vNext}
\label{sec:vnext}

@@

\section{Conclusion}
\label{sec:conclusion}

@@

\section{Acknowledgments}

We thank our shepherd Haryadi Gunawi for his valuable guidance, and the reviewers for their constructive comments. We also thank Ankush Desai from UC Berkeley, and Rich Draves, David Goebel, David Nichols and SW Worth from Microsoft, for their valuable feedback and discussions at the various stages of this work. We acknowledge that this research was partially supported by a gift from Intel Corporation.

>>>>

\vspace{-1mm}
\section{Case Study: Azure Storage vNext}
\label{sec:vnext}
\vspace{-1mm}

@@

\vspace{-1mm}
\section{Conclusion}
\label{sec:conclusion}

@@

\vspace{-1mm}
\section{Acknowledgments}

We thank our shepherd Haryadi Gunawi for his valuable guidance that significantly improved the paper, and the anonymous reviewers for their constructive comments. We also thank Ankush Desai from UC Berkeley, and Rich Draves, David Goebel, David Nichols and SW Worth from Microsoft, for their valuable feedback and discussions at various stages of this work. We acknowledge that this research was partially supported by a gift from Intel Corporation.

### 2016-01-24 related.tex
updates

Formal methods have been successfully used in industry to verify the correctness of distributed protocols. A recent notable example is the use of TLA+~\cite{lamport1994temporal} by the Amazon Web Services team~\cite{newcombe2015aws}. TLA+ is an expressive formal specification language that can be used to design and verify concurrent programs via model checking. A limitation of TLA+, as well as other similar specification languages, is that they are applied on a model of the system and not the actual system. Even if the model is verified, the gap between the real-world implementation and the verified model is still significant, so implementation bugs are still a realistic concern.

Another formal approach is Verdi~\cite{wilcox2015verdi}, a framework for writing and verifying distributed systems in Coq~\cite{barras1997coq}. Verdi generates OCaml code from the verified Coq system, which can be then used for execution. In contrast, \psharp performs bounded testing on a system already written in \csharp, which in our experience lowers the bar for adoption by engineering teams. Verdi does not currently support detecting liveness property violations, an important class of bugs in distributed systems.

>>>>

Formal methods have been successfully used in industry to verify the correctness of distributed protocols. A notable example is the use of TLA+~\cite{lamport1994temporal} by the Amazon Web Services team~\cite{newcombe2015aws}. TLA+ is an expressive formal specification language that can be used to design and verify concurrent programs via model checking. A limitation of TLA+, as well as other similar specification languages, is that they are applied on a model of the system and not the actual system. Even if the model is verified, the gap between the real-world implementation and the verified model is still significant, so implementation bugs are still a realistic concern.

More recent formal approaches include the Verdi~\cite{wilcox2015verdi} and IronFleet~\cite{hawblitzel2015ironfleet} frameworks. In Verdi, developers can write and verify distributed systems in Coq~\cite{barras1997coq}. After the system has been successfully verified, Verdi translates the Coq code to OCaml, which can be then compiled for execution. Verdi does not currently support detecting liveness property violations, an important class of bugs in distributed systems.
In IronFleet, developers can build a distributed system using the Dafny~\cite{leino2010dafny} language and program verifier. Dafny verifies system correctness using the Z3~\cite{de2008z3} SMT solver, and finally compiles the verified system to a .NET executable.
In contrast, \psharp performs bounded testing on a system already written in .NET, which in our experience lowers the bar for adoption by engineering teams.

### 2016-01-24 vnext.tex
updates

\begin{figure}[t]
\centering
\includegraphics[width=\linewidth]{img/azurestore}
\vspace{-5mm}
\caption{Top-level components for extent management in Microsoft Azure Storage vNext.}
\label{fig:vnext}
\vspace{-2mm}
\end{figure}

@@

This bug proved difficult to identify, reproduce and troubleshoot. First, an extent never being repaired is \emph{not} a property that can be easily checked. Second, the bug appeared to manifest only in very long executions. Finally, by the time that the bug did manifest, very long execution traces had been collected, which made manual inspection tedious and ineffective.
%To uncover this bug, as well as many other tricky bugs, the vNext developers are in constant search of a generic and systematic approach for testing distributed systems.

\begin{figure}[t]
\centering
\includegraphics[width=\linewidth]{img/modeled_vnext}
\vspace{-5mm}
\caption{Real Extent Manager with its \psharp test harness (each box represents one \psharp machine).}
\label{fig:azurestoremodel}
\vspace{-2mm}
\end{figure}

@@

  [OnEvent(TimerTickEvent, ProcessExtentRepair)]
  void ProcessExtentRepair() {
    // extent repair loop driven by external timer
    ExtMgr.ProcessEvent(new ExtentRepairEvent());
  }
}
\end{lstlisting}
\vspace{-3mm}
\caption{The real Extent Manager is wrapped inside the \texttt{ExtentManager} \psharp machine.}
\label{fig:wrap_target}
\vspace{-1mm}
\end{figure}

@@

\begin{figure}[t]
\centering
\includegraphics[width=.95\linewidth]{img/extent_manager}
\vspace{-2mm}
\caption{Internal components of the real Extent Manager in Microsoft Azure Storage vNext.}
\label{fig:extentmanager}
\vspace{-2mm}
\end{figure}

@@

// modeled engine for intercepting Extent Manager messages
class ModelNetEngine : NetworkEngine {
  public override void SendMessage(Socket s, Message msg) {
    // intercept and relay Extent Manager messages
    PSharp.Send(TestingDriver, new ExtMgrMsgEvent(), s, msg);
  }
}
\end{lstlisting}
\vspace{-4mm}
\caption{Modeled vNext network engine.}
\label{fig:enginecode}
\vspace{-2mm}
\end{figure}

@@

  void InjectNodeFailure() {
    // nondeterministically choose an EN using P#
    var node = (Machine)PSharp.Nondet(ExtentNodes);    
    PSharp.Send(node, new FailureEvent()); // fail chosen EN
  }
}
\end{lstlisting}
\vspace{-4mm}
\caption{Code snippet of the TestingDriver machine.}
\label{fig:testing_driver}
\vspace{-4mm}
\end{figure}

@@

  // hot state: repairing
  hot state Repairing {
    [OnEvent(ExtentRepairedEvent, ProcessRepairCompletion)]
    void ProcessRepairCompletion(ExtentNodeMachine en) {
      ExtentNodesWithReplica.Add(en);
      if (ReplicaCount == Harness.REPLICA_COUNT_TARGET)
        jumpto Repaired;
    }
  }
}
\end{lstlisting}
\vspace{-5mm}
\caption{The RepairMonitor liveness monitor.}
\label{fig:monitor}
\vspace{-2mm}
\end{figure}

>>>>

\begin{figure}[t]
\centering
\includegraphics[width=\linewidth]{img/azurestore}
\vspace{-6mm}
\caption{Top-level components for extent management in Microsoft Azure Storage vNext.}
\label{fig:vnext}
\vspace{-2mm}
\end{figure}

@@

This bug proved difficult to identify, reproduce and troubleshoot. First, an extent never being repaired is \emph{not} a property that can be easily checked. Second, the bug appeared to manifest only in very long executions. Finally, by the time that the bug did manifest, very long execution traces had been collected, which made manual inspection tedious and ineffective.

\begin{figure}[t]
\centering
\includegraphics[width=\linewidth]{img/modeled_vnext}
\vspace{-6mm}
\caption{Real Extent Manager with its \psharp test harness (each box represents one \psharp machine).}
\label{fig:azurestoremodel}
\vspace{-2mm}
\end{figure}

@@

  [OnEvent(TimerTickEvent, ProcessExtentRepair)]
  void ProcessExtentRepair() {
    // extent repair loop driven by external timer
    ExtMgr.ProcessEvent(new ExtentRepairEvent());
  }
}
\end{lstlisting}
\vspace{-3mm}
\caption{The real Extent Manager is wrapped inside the \texttt{ExtentManager} \psharp machine.}
\label{fig:wrap_target}
\vspace{-3mm}
\end{figure}

@@

\begin{figure}[t]
\centering
\includegraphics[width=.95\linewidth]{img/extent_manager}
\vspace{-3mm}
\caption{Internal components of the real Extent Manager in Microsoft Azure Storage vNext.}
\label{fig:extentmanager}
\vspace{-3mm}
\end{figure}

@@

// modeled engine for intercepting Extent Manager messages
class ModelNetEngine : NetworkEngine {
  public override void SendMessage(Socket s, Message msg) {
    // intercept and relay Extent Manager messages
    PSharp.Send(TestingDriver, new ExtMgrMsgEvent(), s, msg);
  }
}
\end{lstlisting}
\vspace{-5mm}
\caption{Modeled vNext network engine.}
\label{fig:enginecode}
\vspace{-3mm}
\end{figure}

@@

  void InjectNodeFailure() {
    // nondeterministically choose an EN using P#
    var node = (Machine)PSharp.Nondet(ExtentNodes);
    // fail chosen EN
    PSharp.Send(node, new FailureEvent());
  }
}
\end{lstlisting}
\vspace{-3mm}
\caption{Code snippet of the TestingDriver machine.}
\label{fig:testing_driver}
\vspace{-1mm}
\end{figure}

@@

  // hot state: repairing
  hot state Repairing {
    [OnEvent(ExtentRepairedEvent, ProcessRepairCompletion)]
    void ProcessRepairCompletion(ExtentNodeMachine en) {
      ExtentNodesWithReplica.Add(en);
      if (ReplicaCount == Harness.REPLICA_COUNT_TARGET)
        jumpto Repaired;
    }
  }
}
\end{lstlisting}
\vspace{-4mm}
\caption{The RepairMonitor liveness monitor.}
\label{fig:monitor}
\vspace{-2mm}
\end{figure}
